%-------------------------
% Resume in Latex
% Author : Mark Joseph Balagtas
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
% \newcommand{\resumeItem}[2]{
%   \item\small{
%     \textbf{#1}{: #2 \vspace{-2pt}}
%   }
% }

\newcommand{\resumeItem}[1]{\item\small{#1}}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

% \newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItem}[1]{\item{\small#1\vspace{-4pt}}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Huge Mark Joseph Balagtas} & Email : \href{mailto:mark.joseph.balagtas@outlook.com}{mark.joseph.balagtas@outlook.com}\\
    \textbf{\Large Software Developer} & Mobile : 
    \href{tel:+639231407446}{+63 923-140-7446}\\ {Pampanga, Philippines} &
  \href{https://github.com/514sh}{Github: github.com/514sh}
\end{tabular*}


%-----------PROFESSIONAL SUMMARY-----------------
\section{Professional Summary}
\resumeItemListStart
\resumeItem
{Highly motivated and resourceful software developer with over a year of experience in software development and maintenance.} 
\resumeItem
{A problem solver with a strong focus on delivering effective solutions.}
\resumeItemListEnd

%-----------PROFESSIONAL EXPERIENCE-----------------
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Accenture Inc.}{Taguig City, Philippines}
{Associate Software Engineer}{April 2022 - August 2023}
\resumeItemListStart
\resumeItem
{Played a pivotal role as a Level 2 Support Specialist in the maintenance and support of a critical middleware application used globally.}
\resumeItem
{Provided comprehensive support for the middleware application, which is developed using Oracle SOA and Java for its services.}
\resumeItem
{Resolved a wide range of issues related to the application, including change tickets, incident tickets, and request items tickets, raised by application users, developers, and testers.}
\resumeItem
{Collaborated closely with cross-functional teams to identify, troubleshoot, and resolve complex technical issues within defined service level agreements (SLAs).}
\resumeItem
{Deployed updates and enhancements to the software application, ensuring seamless functionality and performance improvements.}
\resumeItem
{Monitored and assessed CPU utilization and server states, promptly taking corrective actions when necessary to maintain optimal application performance.}
\resumeItem
{Contributed to the continuous improvement of support processes, helping streamline issue resolution and reduce downtime.}
\resumeItemListEnd

\resumeSubheading
{Traceserv}{Quezon City, Philippines}
{Cadet Network Engineer}{April 2021 - September 2021}
\resumeItemListStart
\resumeItem
{Performed basic commissioning, troubleshooting, system testing, and hardware testing of Huawei equipment, including ATN910C and ATN910C-G.}
\resumeItem
{Reported to the Globe Technology Network Operations Center for pre-validation and post-validation of voice and data.}
\resumeItem
{Conducted equipment upgrades from ATN910B to ATN910C router series.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Don Honorio Ventura State University}{Bacolor, Pampanga, Philippines}
{Bachelor of Science in Electronics Engineering}{June 2015 - June 2020}
\resumeSubHeadingListEnd

%-----------ADDITIONAL EXPERIENCE-----------------
\section{Additional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Clients from UAE}{Remote}
{Freelance Data Automation Specialist}{March 2023 - Present}
\resumeItemListStart
\resumeItem
{Managed end-to-end data processing for clients, including data input from txt files and generating output files based on client specifications.}
\resumeItem
{Developed custom Python3 scripts using an object-oriented approach to automate data analysis tasks, improving efficiency and accuracy.}
\resumeItem
{Created executable (.exe) applications using PyInstaller to run the Python scripts independently on various systems.}
\resumeItem
{Integrated automated communication using WhatsApp to deliver output data to clients, enhancing real-time communication and client satisfaction.}
\resumeItemListEnd

\resumeSubheading
{Macrin.ph}{Makati City, Philippines}
{Intern (IT)}{April 2019 - May 2019}
\resumeItemListStart
\resumeItem
{Developed and debugged software applications in an agile environment.}
\resumeItem
{Participated in daily scrum meetings.}
\resumeItemListEnd



\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeSubheading
{\href{http://www.flavorfulfinds.xyz/}{Flavorful Finds}}{Domain: flavorfulfinds.xyz}
{A recipe finder web application}{}
\resumeItemListStart
\resumeItem
{A web app that allows users to search for recipes by ingredients or recipe title.}
\resumeItem
{Features user account functionality for creating accounts, logging in, and storing favorite recipes.}
\resumeSubItem
{Technologies used}
\resumeSubHeadingListStart
\resumeItem{Frontend: React, Chakra UI} 
\resumeItem{Backend: Flask} 
\resumeItem{Database: PostgreSQL, Excel}
\resumeItem{Containerization: Docker, Docker Compose} 
\resumeItem{Web Servers: Nginx}
\resumeItem{Cloud Services: AWS (EC2, Route 53, S3)} 
\resumeItem{Version Control: Git, Github}
\resumeSubHeadingListEnd
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------CERTIFICATES-----------------
\section{Certificates}
\resumeSubHeadingListStart

\resumeSubheading
{\href{https://studies.cs.helsinki.fi/stats/api/certificate/docker2023/en/53830ae5415b59882a9ecb3bc8052552}
{Certificate Course in DevOps with Docker}}{University of Helsinki}
{\href{https://devopswithdocker.com}{devopswithdocker.com}}{2023}
\resumeSubheading
{\href{https://studies.cs.helsinki.fi/stats/api/certificate/fs-cicd/en/ced81c9b6eb5147f507b806893b95c4d}
{Certificate Course in CI/CD}}{University of Helsinki}
{\href{https://fullstackopen.com/en/part11}{fullstackopen.com/part11}}{2023}
\resumeSubheading
{\href{https://certificates.mooc.fi/validate/ynptl4uyzlh}
{Certificate Course in Java Programming I and Java Programming II}}{University of Helsinki}
{\href{https://java-programming.mooc.fi/}{java-programming.mooc.fi/}}{2022}
\resumeSubheading
{\href{https://studies.cs.helsinki.fi/stats/api/certificate/fullstackopen/en/d143d632300e29c5c498bce5528df5d7}{Certificate Course in Fullstack Development}}{University of Helsinki}
{\href{https://fullstackopen.com/en/}{fullstackopen.com}}{2021 - 2022}

\resumeSubHeadingListEnd

%-----------LANGUAGES-----------------
\section{Languages}
\resumeSubHeadingListStart
\resumeItem{English - (Fluent)} 
\resumeItem{Tagalog - (Native)}
\resumeSubHeadingListEnd

\end{document}
