%-------------------------
% Resume in Latex
% Author : Michael Joshua Balagtas
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
% \newcommand{\resumeItem}[2]{
%   \item\small{
%     \textbf{#1}{: #2 \vspace{-2pt}}
%   }
% }

\newcommand{\resumeItem}[1]{\item\small{#1}}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

% \newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItem}[1]{\item{\small#1\vspace{-4pt}}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Huge Michael Joshua Balagtas} & Email : \href{mailto:balagtasmichaeljoshua@gmail.com}{balagtasmichaeljoshua@gmail.com}\\
    \textbf{\Large Back End Developer} & Mobile : 
    \href{tel:+639054312885}{+63 905-431-2885}\\ {Pampanga, Philippines} &
  \href{https://github.com/PitsMB}{Github: github.com/PitsMB}
\end{tabular*}


%-----------PROFESSIONAL SUMMARY-----------------
\section{Professional Summary}
\resumeItemListStart
\resumeItem
{Highly motivated and resourceful software developer with great attention to detail, eager to contribute to dynamic teams and innovative projects.} 
\resumeItem
{Computer Science graduate with hands-on experience in backend development, RESTful API design, and proficiency in Python, PHP, and MySQL.}
\resumeItem
{A problem solver with a strong focus on delivering effective solutions.}
\resumeItemListEnd

%-----------PROFESSIONAL EXPERIENCE-----------------
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Pixel8}{Remote}
{Backend Developer(Intern)}{February 2024 - April 2024}
\resumeItemListStart
\resumeItem
{Developed backend solutions for retail enterprises using PHP and Composer, with a focus on object-oriented programming.}
\resumeItem
{Designed and implemented RESTful APIs to support scalable web applications.}
\resumeItem
{Conducted unit testing to ensure code quality and reliability.}
\resumeItem
{Performed API testing using Insomnia and Codeception to validate functionality.}
\resumeItem
{Managed version control using Git and GitLab in an Agile development environment.}
\resumeItem
{Worked with MySQL databases to design, manage, and optimize data storage.}
\resumeItem
{Created comprehensive API documentation to facilitate developer collaboration and integration.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart

% \resumeItemListStart
% \resumeItem
% {}
% \resumeItemListEnd

\resumeSubheading
{Don Honorio Ventura State University}{Bacolor, Pampanga, Philippines}
{Bachelor of Science in Computer Science}{October 2020 - August 2024}
\resumeItemListStart
\resumeItem
{Awarded best thesis for delivering an outstanding project that demonstrated innovation and comprehensive research.}
\resumeItem
{Thesis project: DHVChat: A Web-based Intelligent Chat Assistant for the Admission Office using Natural Language Proccessing}
\resumeItem
{Other project: DHVSU E-Library: A Web-based Library Management System}
\resumeItemListEnd

\resumeSubheading
{Senior High School in Apalit(Stand-Alone-1)}{Apalit, Pampanga, Philippines}
{TVL Track ICT - Specialization in Computer System Servicing}{June 2018 - March 2020}
\resumeItemListStart
\resumeItem
{NCII: Computer System Servicing}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------ADDITIONAL EXPERIENCE-----------------
\section{Additional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Clients from UAE}{Remote}
{Freelance Data Automation Associate}{March 2023 - Present}
\resumeItemListStart
\resumeItem
{Managed end-to-end data processing for clients, including data input from txt files and generating output files based on client specifications.}
\resumeItem
{Effectively troubleshoot and resolve client issues to enhance satisfaction and ensure optimal service delivery.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeSubheading
{\href{https://github.com/PitsMB/e-kanban}{E-kanban}}{Domain: github.com/PitsMB/e-kanban}
{Developed a task management web application featuring a Kanban interface.}{}
\resumeItemListStart
\resumeItem
{An Issuer (admin user) can assign tasks, while machine operators update the status of each product (coil) after each process stage. Enabling streamlined product and process tracking.}
\resumeItem
{Task assignment and status update system that supports real-time, process-oriented workflows.}
\resumeItem
{Search functionality for admin users to locate and manage specific products efficiently.}
\resumeSubItem
{Technologies used}
\resumeSubHeadingListStart
\resumeItem{Frontend: CSS, HTML, and Jinja} 
\resumeItem{Backend: Python(Flask)} 
\resumeItem{Database: MySQL}
\resumeItem{Version Control: Git, Github}
\resumeSubHeadingListEnd
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------CERTIFICATES-----------------
\section{Certificates}
\resumeSubHeadingListStart

\resumeSubheading
{\href{https://certificates.mooc.fi/validate/w6qn5hpzdu}
{Certificate Course in Python Programming}}{University of Helsinki}
{\href{https://programming-24.mooc.fi/}{Python Programming MOOC}}{2024}
% \resumeSubheading
% {\href{https://studies.cs.helsinki.fi/stats/api/certificate/fs-cicd/en/ced81c9b6eb5147f507b806893b95c4d}
% {Certificate Course in CI/CD}}{University of Helsinki}
% {\href{https://fullstackopen.com/en/part11}{fullstackopen.com/part11}}{2023}
% \resumeSubheading
% {\href{https://certificates.mooc.fi/validate/ynptl4uyzlh}
% {Certificate Course in Java Programming I and Java Programming II}}{University of Helsinki}
% {\href{https://java-programming.mooc.fi/}{java-programming.mooc.fi/}}{2022}
% \resumeSubheading
% {\href{https://studies.cs.helsinki.fi/stats/api/certificate/fullstackopen/en/d143d632300e29c5c498bce5528df5d7}{Certificate Course in Fullstack Development}}{University of Helsinki}
% {\href{https://fullstackopen.com/en/}{fullstackopen.com}}{2021 - 2022}

\resumeSubHeadingListEnd

%-----------LANGUAGES-----------------
\section{Languages}
\resumeSubHeadingListStart
\resumeItem{English - (Fluent)} 
\resumeItem{Tagalog - (Native)}
\resumeSubHeadingListEnd

\end{document}
